ShabbyPages: A Recipe for Repeatable, Synthetic, Modern Document Images

### 2023-01-24 paper/paper.tex

\begin{figure}
\includegraphics[width=\textwidth]{Article_Hero_Picture_Shadow.png}
\caption{Example ShabbyPages image, before and after augmentation.} \label{fig1}
\end{figure}

@@

\begin{table}
\centering
\caption{ShabbyPages Statistics}\label{tab1}
\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
\hline
Statistic & Value \\
\hline
Images & 6202 \\
DPI & 150 \\
Max image size & \_ \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[]
    \centering
    \caption{Image restoration performance between NoisyOffice-trained and ShabbyPages-trained NAFNet binarizing denoisers on cross-validation task}
    \scalebox{0.81}{
    \begin{tabular}{llll}
    \toprule
    \textbf{Training Set} & \textbf{Test Set} & \textbf{SSIM} & \textbf{RMSE} & \textbf{PSNR} \\
        \midrule
        \textsf{ShabbyPages} & \textsf{ShabbyPages} & \textsf{0.9255905809319086} & \textsf{2.987994328426575} & \textsf{39.29266235129017}\\
        \textsf{SimulatedNoisyOffice} & \textsf{RealNoisyOffice} & \textsf{0.9866020337197627} & \textsf{3.8045857559449296} & \textsf{36.73658388839052}\\
        \textsf{ShabbyPages} & \textsf{RealNoisyOffice} & \textsf{0.9465069385860134} & \textsf{3.2046770685272117} & \textsf{38.097843772060855}\\
        \textsf{SimulatedNoisyOffice} & \textsf{ShabbyPages} & \textsf{0.8105023745816482} & \textsf{5.38408321532059} & \textsf{34.56195157529838}\\
        \bottomrule
    \end{tabular}}
    \label{tab:binarization_results}
\end{table}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.98\columnwidth, frame]{Article_Hero_Picture_Shadow.png}
\caption{Example ShabbyPages image, before (left side) and after augmentationi (right side).} \label{fig1}
\end{figure}

@@

\begin{table}
    \centering
    \caption{ShabbyPages dataset statistics.}\label{tab1}
    \begin{tabular}{@{\hspace{2em}}l@{\qquad}@{\hspace{2em}}l@{\qquad}}
        \toprule
        \textbf{Statistic} & \textbf{Value} \\
        \midrule
        Num. Images & 6202 \\
        DPI & 150 \\
        Max image size & --- \\
    \bottomrule
    \end{tabular}
\end{table}

@@

\begin{table}[]
    \centering
    \caption{Document image binarization performance of a NAFNet model trained and tested on ShabbyPages and NoisyOffice.}
    %\caption{Document image binarization performance between NoisyOffice-trained and ShabbyPages-trained NAFNet binarizing de    noisers on cross-validation task}
    \scalebox{0.9}{
    \begin{tabular}{lllll}
    \toprule
    \textbf{Training Set~~} & \textbf{Test Set} & \textbf{SSIM$\uparrow$~} & \textbf{RMSE$\downarrow$~} & \textbf{PSNR$\uparrow$} \\
        \midrule
        \textsf{ShabbyPages} & \textsf{ShabbyPages} & 0.926 & 2.99 & 39.3\\
        \textsf{NoisyOffice-sim} & \textsf{NoisyOffice-real~} & 0.987 & 3.80 & 36.7\\
        \textsf{ShabbyPages} & \textsf{NoisyOffice-real} & 0.947 & 3.20 & 38.1\\
        \textsf{NoisyOffice-sim} & \textsf{ShabbyPages} & 0.811 & 5.38 & 34.6\\
        \bottomrule
    \end{tabular}}
    \label{tab:binarization_results}
\end{table}
